\documentclass{moderncv}
\moderncvtheme{classic}

\nopagenumbers{}

\firstname{Le}
\familyname{Yang}
\title{Senior software engineer}
\mobile{18742026096}
\email{qtxzh0125@gmail.com, yangle0125@qq.com}
\extrainfo{https://github.com/yang-le}

\begin{document}
\maketitle

\section{Education}
\cvline{2007 - 2011}{}
\cvline{School}{Hebei university of science and technology}
\cvline{Major}{Software engineering}

\section{Skill}
\cvline{}{10 years working/coding experience of C/C++.}
\cvline{}{As a 15 years Linux user, familiar with Linux and its kernel.}
\cvline{}{3 years working experience of Android HAL.}
\cvline{}{3 years working experience of ADAS.}
\cvline{}{Java, Python, Kotlin, JavaScript, Latex and Verilog.}

\section{Working experience}
\cvline{2011 - 2014}{Software engineer in Neusoft}
\cvline{}{Multimedia player and digital camera for Panasonic.}
\cvline{2015 - 2018}{Senior software engineer in Neusoft}
\cvline{}{ADAS platform.}
\cvline{2019 - 2022}{Senior software engineer in Neusoft}
\cvline{}{Android platform, HAL.}
\cvline{2022 - 2023}{Senior software engineer in ReachAuto, Neusoft}
\cvline{}{Linux platform, BSP.}

\section{Personal projects}
\cvline{riscv cpu}{A Verilog implementation of a RISC-V CPU that can pass the official tests.}
\cvline{cnet}{A deep learning framework using C language.}
\cvline{myOS}{A toy operating system that supports mouse.}
\cvline{DLAN Demo}{An android app that can project smartphone screen to TV, using Kotlin and Compose.}

\end{document}
